%!TEX root = ../dissertation.tex

\chapter{Introduction}
\label{chapter:introduction}
In recent years, computing is becoming more ubiquitous in the physical world. This notion where
computational elements are embedded seamlessly in ordinary objects that are connected through a
continuous network was introduced many years ago \cite{weiser1991computer}. The progress
towards ubiquitous computing has been slower than expected, technology advances such as the mobile
Internet contributes to achieve this vision in which computational devices are able to communicate
between themselves from any part of the world \cite{gubbi2013internet}. In this vision, an ubiquitous
system is composed of physical items that are continuously connected to the virtual world and can act as
remotely and physical access points to Internet Services \cite{mattern2010internet}.\\

However, there are some challenges that must be addressed in order to make these \gls{ubicomp} systems
truly ubiquitous \cite{caceres2012ubicomp}. An important concern regards about ubiquitous data: \textit{Where it is located?},
\textit{Who can access it?} and \textit{How much time this data should persist?}. Also, ubiquitous systems
are constantly interacting with the surrounding environment. Thus, these systems need to understand
the context in that they are inserted and also to adapt to the changes that occur in this environment.
Another import concern regards about the infrastructure burden of the ubiquitous systems. These
systems requires low-latency interaction with users and environments, which implies that at least part
of an \gls{ubicomp} application needs to be tightly bounded to the local infrastructure of the interacting
environment. This requirement for local infrastructure can be a barrier in the adoption of ubiquitous
systems in a large-scale perspective.\\

This ubiquitous world is close to becoming reality thanks to the Utility Computing in the cloud
and the \gls{IoT}. In one hand, the utility computing provides the illusion of infinite computing
resources available on demand to the public users \cite{armbrust2010view}, which helps to reduce the
infrastructure burden of the ubiquitous systems. In the other hand, the \gls{IoT} aims to solve a key
problem in wider adoption of ubiquitous systems, the tight coupling with a particular embedded
infrastructure. With the \gls{IoT} a variety of \textit{objects} or \textit{things} - such as \gls{RFID},
tags, sensors, actuators, etc. - will be able to interact with each other and cooperate with the
surrounding \textit{things} to reach common goals \cite{atzori2010internet}.\\

% Applications
\section{Applications}
\label{sec:applications}
The Internet of Things offers a great potential that makes possible the development of a huge number
of applications. There are several environments and domains where the \gls{IoT} applications will be
able to improve the quality of life of the people that lives and works in these environments and also
will provide competitive advantage against current solutions. Currently, the application domains that
promises to play a big role in the adoption of \gls{IoT} are:
% Smart Environments
\subparagraph{Smart Places} are environments that uses the intelligence of the objects within itself
to become a more comfortable and efficient environment. For instance, a room that has its temperature
adapted according the weather, an office that has its lights adapted according the time of the day and
an automated industrial plant where its is possible to monitoring the production progress and to see
the  possible side-effects of a production delay due to a malfunction in a device.
% Logistics
\subparagraph{Logistics} applications are able to perform real-time information processing based
on technologies such as \gls{RFID} and \gls{NFC}. This information allows to achieve real-time monitoring
of almost every phase of the supply chain, ranging from raw material purchasing, transportation,
storage, distribution and after-sales services.
% Transportation
\subparagraph{Transportation} covers a wide area, since personal vehicles from trains, mobile ticketing
and transportation of goods. Cars, trains and buses equipped with sensors, actuators and computational
power are able to provide information about the status of the vehicle, improve the navigation and even
to perform collision avoidance. Regarding the transportation of goods, it is possible to monitoring
the conservation status of perishable goods - temperature, humidity, etc. -  during its transportation.
In public transportation, NFC tags can be used to provide information about the available services
- costs, schedule, etc.
% Healthcare
\subparagraph{Healthcare} is a domain that can benefit in a significant way from the \gls{IoT}
technologies. For instance, \gls{RFID} tags can be used to monitoring the position of patients,
hospital staff and also to control the inventory of materials. Sensors can be used to monitoring
in real-time patient conditions, hospital environment conditions - temperature, air quality, etc.
Moreover, these technologies will provide the ability to perform patient identification, staff authentication,
access control and also to perform automatic data collection in order to improve the efficiency of
the operations in the hospitals.
% Motivation
\section{Motivation}
\label{section:motivation}
The recent progress in the utility computing and the Internet of Things has been contributing to grow the
\gls{ubicomp} infrastructure. However, it is possible to identify new challenges \cite{caceres2012ubicomp}
for the construction of ubiquitous systems that arises from the integration of the Internet of Things
in the utility computing:

% Challenges
\begin{itemize}
  % Low-latency Interaction
  \item \textbf{Low-latency Interaction} is a key requirement of \gls{IoT} systems. This requires that
  both network access latency and data transmission latency be reduced. However, in cloud-based solutions,
  part of the system's infrastructure is moved to the cloud - for instance the middleware layer,
  which is responsible for processing the information and take automatic decisions based on the results
  - is not possible to guarantee that this cloud-based approach will be met the low-latency requirements
  of \gls{IoT} systems.
  % Scalable Data Storage
  \item \textbf{Data} is continuously generated by the \textit{things} that composes the \gls{IoT}
  system. These data must be stored, processed and presented in a seamless and efficient way. Several
  middleware solutions for \gls{IoT} \cite{floerkemeier2007rfid}\cite{eisenhauer2010hydra}\cite{de2008socrades}
  rely on consistent transactions supported by \glspl{RDBMS}, which unfortunately is not scalable
  \cite{hofmann2010cloud}. Since there is no industrial-grade solution for applications that rely on
  consistent transactions to write in multiple nodes at the same time, running high-volume, mission-critical
  transactional systems in the cloud is not a viable option.
  % Infrastructure Provisioning
  \item \textbf{Infrastructure Provisioning} usually was performed in a physical, isolated and vertical
  manner, in which hardware, networks, middleware and application logics are tightly coupled. Recently,
  \gls{IoT} has been adopted more and more in business and tends to weave into our daily life through the smart cities
  \cite{caragliu2011smart}\cite{schaffers2011smart}, this provisioning model presents some limitations
  that makes the delivery of new services an inefficient process, since that each time the same process
  has to be repeated to develop and deploy a new vertical solution.
  % Management
  \item \textbf{Management} of IoT systems is an issue that must be carefully addressed. In one hand
  is already proved that end-users are unable to manage their own personal computers systems well
  \cite{doll1988measurement}. Since there is no reason to believe that they will had a better
  performance at managing a much more complex system - such as an \gls{IoT} system - is reasonable to
  assume that service providers will perform the management of the services . In the other hand, if we
  consider applications that are deployed in large-scale - such as smart cities - these managed
  services introduces new questions that must be answered. For instance, who will pay for this
  services and who will control this services?
  % Investment
  \item \textbf{Investment} in infrastructure is a relevant part of building an \gls{IoT} system,
  is this system deployed in a an small business or in an entire city. Is reasonable to assume that
  these investments need to be repaid. For instance, for businesses the return of investment is
  achieved with the improvement of its business processes, which can help to reduce the manufacturing
  cost of goods, to increase the efficiency of the supply chain, etc. However, for a large-scale
  system that is available for the general public a new model that is beneficial for both users and
  providers need to be established.
\end{itemize}

We believe that finding a solution for these problems is essential for the adoption of \gls{IoT} systems
in a large-scale perspective. However, some of these problems has a socio-economical nature - such as
management and investment of \gls{IoT} systems - and will take time to resolve this issues.

% Topic Overview
\section{Topic Overview}
\label{section:overview}
Recently a lot of research and effort has been dedicated to solve these existing problems. In this
section we will present a summary of the most relevant work that address to solve the problems of
converging the Internet of Things and the utility computing:

% Infrastructure Provisioning
\subsection{Infrastructure Provisioning}
\label{sub:provisioning}
The research area for infrastructure provisioning of IoT solutions is the one that presents the most
notable progress until now.

% Soldatos
\subparagraph{Soldatos} et al. \cite{soldatos2012convergence} presented the idea of converging the IoT
and the utility computing in the cloud. The proposed architecture is the core concept of the OpenIoT
Project\footnote{http://openiot.eu}, and is based on CoAP \cite{shelby2014constrained} and linked data.
The cloud is used at infrastructure level, which allows to measure the utility of the services provided
by inter-connected objects.
% Distefano
\subparagraph{Distefano} et al. \cite{distefano2012enabling} proposed a conceptual architecture by mapping various
elements in both clouds and IoT to the three layers of cloud architecture (\gls{PaaS}, \gls{SaaS} and \gls{IaaS}).
In this proposal IoT resources are provided voluntarily by their owners, while management functions
- such as node management and policy enforcement - are viewed as peer functions of cloud infrastructure
management. IoT resources and cloud infrastructure are mashed up for applications, which are delivered
through \gls{SaaS}.
% CloudThings
\subparagraph{CloudThings} \cite{zhou2013cloudthings} is an architecture that uses a common
approach to integrate Internet of Things and Cloud Computing. The proposed architecture is an online
platform which accommodates \gls{IaaS}, \gls{PaaS}, \gls{SaaS} and allows system integrators and
solution providers to leverage the complete application infrastructure for developing, operating
and composing applications and services.
% IoT PaaS
\subparagraph{Li} et. al \cite{li2013efficient} proposed IoT PaaS, a cloud platform that supports
scalable IoT service delivery. Solution providers are able to deliver new solutions by leveraging
computing resources and platform services - domain mediation, application context management, etc.
- on the cloud. The proposed architecture aims to enable virtual vertical service delivery, for that
it has a multi-tenant nature which is designed to help at the isolation of the environments of
different solutions.

% Scalable Data Storage
\subsection{Scalable Data Storage}
\label{sub:data_storage}
Since that no general solution for scalable data storage and retrieval in the cloud was developed,
cloud providers started to implement its own solutions.

\subparagraph{Google Big Table, Facebook Cassandra and  Amazon Dynamo} \cite{chang2008bigtable} \cite{lakshman2010cassandra}
\cite{decandia2007dynamo} are key-value stores - \gls{NoSQL} databases - that has the ability to horizontally scale - i.e,
distribute both data and load of simple operations through many servers - but it has a weaker concurrency model
than the ACID transactions of most \glspl{RDBMS} systems \cite{cattell2011scalable}.

\subparagraph{\gls{PIQL}} \cite{armbrust2010piql} is a SQL-like API built to run on top of existing
performance predictable key-value stores, that provides many of the benefits of using a traditional
\gls{RDBMS}, such as the ability to express the queries in a declarative way, automatic data
parallelism, physical data independence and automatic index selection and maintenance, all while
maintaining the soft real-time guarantees on application performance that come from the underlying
key-value store.\\

Recently, some progress has been reached as regards scalable storage for \gls{RDBMS} systems. Although
most of the work still are in development, it is possible to highlight some solutions that are in a more
mature state.

\subparagraph{MySQL Cluster} \cite{ronstrom2004mysql} is an in-memory clustered distributed \gls{RDBMS}. Compared with
the MySQL implementation it works by replacing the InnoDB engine with the NDB - a proprietary
distributed layer from MySQL. MySQL Cluster is built on top of a shared-nothing architecture and includes
features such as failover, node recovery, synchronous data replication and no single point of failure.
MySQL Cluster seem to be the solution that scales to more nodes than other \gls{RDBMS} - 48 is the limit.
However, it was reported that after scaling up to a few dozen nodes it starts to running into
bottlenecks \cite{bunch2010evaluation}.

\subparagraph{VoltDB} \cite{stonebraker2013voltdb} is a \gls{RDBMS} designed for performance and scalability. VoltDB
assumes a multi-node cluster architecture where the tables are partitioned over multiple servers. Tables
can be replicated over servers - e.g. for fast access to data - shards are always replicated -
to recovery the data in case of a node crash - and database snapshots are supported. Currently some
features still are missing - online schema changes are limited and asynchronous \gls{WAN} replication and
recovery are not yet implemented - but in its current implementation VoltDB already presents some
features that improves the performance of SQL execution, as result the number of nodes that are needed
to support a given application load can be reduced in a significant way.

% Low-latency Interaction
\subsection{Low-latency Interaction}
\label{sub:low_latency_interaction}
Finding a general solution for the low-latency requirement of \gls{IoT} systems is not a easy task.
Since there are several application domains, is natural that each application domain requires
that different values for network latency and data transmission latency are guaranteed.

% Objectives
\section{Objectives}
\label{section:objectives}
The objective of this work is to discover if the cloud-based solutions met the requirements of Internet of
Things applications. However, in our view is not reasonable try to find a solution that fulfill the
requirements of all application domains of \gls{IoT} systems.\\

\subsection{Domain}
\label{sub:domain}
In this work our efforts will be focused in determine if a cloud-based solution is suitable
for a smart place that relies on the \gls{RFID} technology. Our smart place is an automated warehouse
where products - which are transported through automated guided vehicles - are tagged with \gls{RFID}
tags that can be identified by \gls{RFID} readers. Through the data collected by these readers is
possible to gather knowledge about the smart place. For instance, is possible determine which products
enters or leaves the warehouse. A complete example of a platform that allows the transformation of
that data into information is Fosstrak\footnote{http://fosstrak.github.io/}, an open source \gls{RFID}
software that implements the \gls{EPC} Network standards.\\

%A possible scenario is where a product is being transported from the warehouse inventory section to
%the processing section and there is a door that separates the two sections. When the reader that is
%close to the door detects that a product is approaching the door, an event is triggered and the
%application middleware is responsible to process this event and take the correct decision, in this
%case it must open the warehouse door. In that case we need to determine if a cloud-based solution
%can met the latency interaction requirements for that smart place, otherwise if these requirements are
%not met, a possible situation is where the automated vehicle crashes with door because the request latency
%was to high and then the door took longer to open than expected.\\

% Document Structure
\section{Thesis Outline}
\label{section:outline}
The remainder of this document is organized as follows:
% Document structure item list
\begin{itemize}
  % Background
  \item \textbf{Chapter \ref{chapter:background}. Background} introduces some key concepts that supports
  our work such as a description of the Fosstrak platform, etc.
  % Solution
  \item \textbf{Chapter \ref{chapter:solution}. Solution} presents the approaches adopted to deploy
  and provisioning the smart place software stack, i.e the software stack required to deploy
  an application based on the Fosstrak platform.
  % Implementation
  \item \textbf{Chapter \ref{chapter:implementation}. Implementation} details the implementation
  for the proposed solution, the provisioning strategies, the virtualization technologies, etc.
  % Evaluation
  \item \textbf{Chapter \ref{chapter:evaluation}. Evaluation} describes the experiments made to meet
  the defined objectives and presents an analysis of its results.
  % Conclusion
  \item \textbf{Chapter \ref{chapter:conclusion}. Conclusion} summarizes the presented work,
  presents the main conclusion and some important research points for future work.
\end{itemize}
