
%!TEX root = ../dissertation.tex

% Introduction
\section{Introduction}
\label{sec:introduction}
The \gls{IoT} is a system composed of physical items or \textit{things} that are continuously
connected to the virtual world and can act as physical access points to Internet Services \cite{mattern2010internet}.
Many times these systems requires low-latency interaction with users and environments, which implies
that at least part of an \gls{IoT} application needs to be tightly bound to the local infrastructure
of the interacting environment. This requirement for local infrastructure can be a barrier in the
adoption of those systems in a large-scale perspective. The Utility Computing in the cloud paradigms
can help to solve this issue by providing the illusion of infinite computing resources available on
demand to the public users \cite{armbrust2010view}. This paradigm can help to reduce the infrastructure
burden of \gls{IoT}, while providing important features such as high availability and high scalability.

% Application Domains
\subsection{Application Domains}
\label{sub:application_domains}
There are several environments and domains where \gls{IoT} applications are expected
to improve the quality of life of the people that live and work in these environments.

% Ambient Intelligence
\textit{Ambient Intelligence} are environments that use the intelligence of the objects within
themselves to become a more comfortable and efficient environment. For instance, an automated industrial
plant where its is possible to monitor the production progress.
% Logistics
In \textit{Logistics}, real-time information processing based on technologies such as \gls{RFID} allows the
monitoring of almost every phase of the supply chain, ranging from raw material purchasing, transportation
and after-sales services.
% Transportation
A large area that is covered by \gls{IoT} is \textit{Transportation}. From personal vehicles to public
transportation, mobile ticketing and transportation of goods. Cars, trains and buses are equipped with
sensors, actuators and computational power that are able to provide information about the status of
the vehicle, improve the navigation and even perform collision avoidance.

To give a more unified view over those domains, we propose the term \textit{smart places},
that can be defined as an environment composed of sensors - e.g. RFID - actuators - e.g. automatic
doors - and computational infrastructure - e.g. servers - that are able to acquire data about the
surrounding environment and use that data to improve the experience of the people interacting with
the place.

% Smart Places Challenges
\subsection{Smart Places Challenges}
\label{sub:challenges}
Challenges \cite{caceres2012ubicomp} for the construction of smart places that resulted from leveraging
part of the smart place infrastructure to the cloud:

% Deployment
\textit{a) Deployment} of smart places usually is performed in an isolated and vertical manner, which
makes the its deployment an inefficient process. Therefore, new provisioning approaches need to be
adopted in order to make the deployment smart place more efficient and scalable.

% Low-latency Interaction
\textit{b) Low-latency Interaction} is a key requirement that requires that both network access
latency and data transmission latency be reduced. However, will a cloud-based
approach able to meet the low-latency requirements of smart place applications?

% Cost
\textit{c) Cost vs. Performance} of smart places infrastructure is an important issue
that can determine if the cloud platform is adequate to support smart places. By
leveraging the smart place infrastructure to the cloud the cost of its infrastructure
can be reduced in a significant amount. However, will be the performance of the
smart place satisfactory when its infrastructure is leveraged to the cloud?

% Objectives
\subsection{Objectives}
\label{sub:objectives}
The objective of this work is to determine if a cloud-based solution can meet the low-latency network
and data storage performance requirements for smart place applications. Our efforts will be engaged in
determine if a cloud-based solution is suitable for a smart warehouses that relies on the RFID technology
\cite{want2006introduction}.

\subsubsection{Example Domain}
\label{subs:domain}
Our example domain is an automated warehouse, where products are tagged with \gls{RFID} tags that
can be identified by \gls{RFID} readers. Through the data collected by these readers is possible to
gather information about the smart place. A complete example of a platform that allows the transformation
of that data into information is Fosstrak\footnote{\url{http://fosstrak.github.io/}}, an open
source \gls{RFID} software that implements the \gls{EPC} Network standards.

To accomplish our objectives, in this work we will follow two approaches and determine which of them
is more adequate to deploy a \gls{RFID} application. The first, is a more traditional approach, where
all the application middleware is provisioned in the cloud. The second is an approach based on the Fog
Computing\cite{bonomi2012fog}, a virtualized platform that is located close to the smart place and
provides network, computing and storage resources between the embedded devices in the physical place
and the traditional cloud.

Since the cloud platform offers flexibility to deploy the applications, we propose a solution that
automates the deployment of \gls{RFID} applications in the cloud regarding the chosen approach:
cloud or fog. Our solution consists in a provisioning mechanism that automates the application
deployment according pre-defined provisioning policies and software images.

The remainder of this document is organized as follows. Section \ref{sec:background} summarizes the
relevant work in the field and introduces the base concepts of our work such as a description of the
Fog Computing paradigm and the Fosstrak platform. In Section \ref{sec:solution} we present the
approaches adopted to deploy and provision the smart place and details the implementation
of the proposed solution. In Section \ref{sec:evaluation} describes the performed evaluation and
presents an analysis of the obtained results and finally in Section \ref{sec:conclusion} we present
the main conclusion and some important research points for future work.
