% -------------------------------------------------------------------------------------------------
% RELATED WORK
% -------------------------------------------------------------------------------------------------
\section{Related Work}
\label{sec:related_work}
As mentioned before, applications for Internet of Things requires an infrastructure that is cost ineffective and
presents a low scalability. Recently, the cloud paradigm allows to leverage the applications infrastructure to
the cloud providers, making possible to increase the application scalability and also to reduce in a significant
way the cost related with the infrastructure.

% ----------------------------------------
% INTERNET OF THINGS AND CLOUD COMPUTING
% ----------------------------------------
In RFID-based IoT applications, Guinard et al. \cite{guinard2011cloud} point out that the
deployment of RFID applications are cost-intensive mostly because they involve the
deployment of often rather large and heterogeneous distributed systems. As a consequence,
these systems are often only suitable for big corporations and large implementations and
do not fit the limited resources of small to mid-size businesses and small scale applications
both in terms of required skill-set and costs. To address this problem, Guinard et al. propose
a cloud-based solution that integrates virtualization technologies and the architecture of
the Web and its services. The case of study consists in a IoT application that uses RFID technology
to substitute existing Electronic Article Surveillance (EAS) technology, such as those used in
clothing stores to track the products. In this scenario they applied the Utility Computing blueprint
to the software stack - Fosstrak - required by the application using the Amazon Web Services platform and the
Amazon EC2 service. To evaluate the Cloud-based solution, two prototypes was successfully
implemented to prove that the pain points of the RFID applications can be relaxed by adopting the
proposed solution.

However, provisioning applications for Internet of Things still is an issue, due to the Virtual Machines
need to be manually configured and the deployment operation of those applications is specific for each
provider.

% ---------------------------------------------
% AWS
% ---------------------------------------------
Amazon Web Services\footnote{http://aws.amazon.com/} (AWS) offers a variety of services that are able
to automate the provisioning of the IT infrastructure at the Amazon EC2 (EC2). VM Import/Export is a
service provided by AWS that enables to import virtual machine images from the development environment
to EC2 instances and export them back to the on-premisies development environment. This offering allows
to leverage the existing investments in the virtual machines that was built to meet the IT security,
configuration management, and compliance requirements by bringing those virtual machines into EC2 as
ready-to-use instances. The instances also can be exported to the on-premises virtualization infrastructure,
allowing to deploy workloads across the IT infrastructure. Another service provided by AWS is Elastic Beanstalk.
Elastic Beanstalk is a service available on AWS that allows to quickly deploy and manage an application in
the AWS cloud. The application is uploaded to AWS, and Elastic Beanstalk automatically handles with the
details of capacity provisioning, load balancing, scaling and application health monitoring. Elastic Beanstalk
supports several types of applications, including Java, Python, Ruby on Rails and Docker containers.

% ---------------------------------------------
% TOSCA
% ---------------------------------------------
TOSCA (Topology and Orchestration Specification for Cloud Applications) \cite{li2013towards} is
proposed in order to improve the reusability of service management processes and automate IoT application
ratified by OASIS in deployment in heterogeneous environments. TOSCA is a new cloud standard to formally
describe the internal topology of application components and the deployment process of Cloud applications.
The structure and management of IT services is specified by a meta-model, which consists of
a \textit{Topology Template}, that is responsible for describing the structure of a service, then there
are the \textit{Artifacts}, that describe the files, scripts and software components necessary to be
deployed in order to run the application, and finally the \textit{Plans}, that defined the management process
of creating, deploying and terminating a service. The correct topology and management procedure can be inferred
by a TOSCA environment just by interpreting the topology template, this is known as ``declarative" approach.
Plans realize an ``imperative" approach that explicitly specifies how each management process should be done.
The topology templates, plans and artifacts of an application are packaged in a Cloud Service Archive (.csar file)
and deployed in a TOSCA environment, which is able to interpret the models and perform the specified management
operations. These .csar files are portable across different Cloud providers, which is a great benefit in terms
of deployment flexibility. To evaluate its feasibility, TOSCA was used in the specification of a typical
application in building automation. an application to control an Air Handling Unit (AHU). The common IoT
components, such as gateways and drivers will be modeled, and the gateway-specific artifacts that are
necessary for application deployment will also be specified. By archiving the previous specifications
and corresponding artifacts into a .csar file, and deploying it in a TOSCA environment, the deployment
of AHU application onto various gateways can be automated. As a newly established standard to counter
growing complexity and isolation in cloud applications environments, TOSCA is gaining momentum in industrial
adoption as well for academic interest.

These solutions allows to automate part of the life-cycle of applications for Internet of Things in the
cloud, which is composed of several stages, starting from installing the sensors
and readers in the smart place, provisioning the infrastructure at the cloud providers, upload the events
that occur in the physical world to the application, monitoring the application health and eventually
deprovisioning the application.
